\documentclass{article}

\begin{document}
\begin{titlepage}
\title{A report about the restaurants and canteens in Makerere University}
\author{Kisekka Genza David 215005443 15/U/6526/PS}
\date{May 20, 2017}
\maketitle

\end{titlepage}

\tableofcontents
\section{Introduction}
Canteens and restaurants in Makerere are one of the busiest places in the public university. Most of them are located in the halls of residence, along main university roads and some can be found right at the faculties of study.\\
Some of the restaurants are privately owned i.e. the ones in halls of residence while others are owned by the University itself. Some of these canteens owned by the university provide services to lecturers and students at subsidiary costs or even for free

\section{Body}
By morning hours most of the restaurants are open in order to service the early students or lecturers though they are mostly busy during lunch time.
 This is an advantage to students and lecturers who stay inside the university as there is an easy access to them. New students who stay outside the university get a hard time knowing the opening times and the locations of the best canteens and restaurants around the university that offer the best quality dishes around.

\section{Recommendation}
To help the non residential and new students around, a platform is to be designed  to provide adequate information about these restaurants and canteens.

The platform is to provide information about the opening and closing times of each restaurant, the physical location of the different restaurants in the university ,an image of the inside or outside of each restaurant/canteen, the GPS coordinates for each restaurant, the dishes and their individual costs that are served daily at the different restaurants, the sitting capacity each restaurant can facilitate and also contact information of the restaurants.

\section{Conclusion}
Restaurants and the canteens around Makerere University provide breakfast, meals and other services that are a vital part in the everyday running of the school and the general lives of the administration, students and lecturers. They therefore should be made as visible as possible and very accessible to all the students, lecturers and other service workers that operate within the school.

\end{document}